The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-11-21 paper/mri_paper.tex
typos

\begin{multline}
\label{ordere3}
\mathcal{D}\partial_T \mathbf{V_1} \, + \, \mathbf{N_3} \, = \, \mathcal{L} \mathbf{V_3} \, + \, \widetilde{\mathcal{L}}_1\partial_Z\mathbf{V_2} \, + \, \widetilde{\mathcal{L}}_2\partial_Z^2\mathbf{V_1} \, \\
- \partial_Z\mathcal{X}\mathbf{V_1} \, - \partial_z^3\mathcal{L}_3\mathbf{V_1}.
\end{multline}

@@

\beq
\begin{split}
\mathbf{V_2} \, & = \, \alpha^2 e^{i2Qz} \mathbb{V}_{22}(x) \, + \, \left|\alpha\right|^2 \mathbb{V}_{20}(x) \, \\
&- \, \partial_Z \alpha \mathbb{V}_{21}(x) e^{iQz} \,- \, \partial_Z \beta \mathbb{U}_{20}(x) + c.c.
\end{split}
\eeq

@@

\beq
\begin{split}
& \mathcal{D} \mathbb{V}_{11} e^{iQz}\partial_T \alpha \, + \, \alpha \left| \alpha^2 \right| \mathbf{N}_{31} e^{iQz} \, + \, \alpha \partial_Z \beta \widetilde{\mathbf{N}}_{31} e^{iQz} \, =  \\
& \, - \partial_Z^2 \alpha \widetilde{\mathcal{L}}_1 \mathbb{V}_{21} e^{iQz} \, + \, \partial_Z^2 \alpha \widetilde{\mathcal{L}}_2 \mathbb{V}_{11} e^{iQz} \, - \, \partial_Z \alpha \mathbb{V}_{11}\mathcal{X}e^{iQz} \, \\
& + \, iQ^3 \alpha \mathcal{L}_3 \mathbb{V}_{11} e^{iQz}.
\end{split}
\eeq

>>>>

\begin{multline}
\label{ordere3}
\mathcal{D}\partial_T \mathbf{V_1} \, + \, \mathbf{N_3} \, = \, \mathcal{L} \mathbf{V_3} \, + \, \widetilde{\mathcal{L}}_1\partial_Z\mathbf{V_2} \, + \, \widetilde{\mathcal{L}}_2\partial_Z^2\mathbf{V_1} \, \\
- \partial_z\mathcal{X}\mathbf{V_1} \, - \partial_z^3\mathcal{L}_3\mathbf{V_1}.
\end{multline}

@@

\beq
\begin{split}
\mathbf{V_2} \, & = \, \alpha^2 e^{i2 k_c z} \mathbb{V}_{22}(x) \, + \, \left|\alpha\right|^2 \mathbb{V}_{20}(x) \, \\
&- \, \partial_Z \alpha \mathbb{V}_{21}(x) e^{i k_c z} \,- \, \partial_Z \beta \mathbb{U}_{20}(x) + c.c.
\end{split}
\eeq

@@

\beq
\begin{split}
& \mathcal{D} \mathbb{V}_{11} e^{i k_c z}\partial_T \alpha \, + \, \alpha \left| \alpha^2 \right| \mathbf{N}_{31} e^{i k_c z} \, + \, \alpha \partial_Z \beta \widetilde{\mathbf{N}}_{31} e^{i k_c z} \, =  \\
& \, - \partial_Z^2 \alpha \widetilde{\mathcal{L}}_1 \mathbb{V}_{21} e^{i k_c z} \, + \, \partial_Z^2 \alpha \widetilde{\mathcal{L}}_2 \mathbb{V}_{11} e^{i k_c z} \, - \, \partial_Z \alpha \mathbb{V}_{11}\mathcal{X}e^{i k_c z} \, \\
& + \, i k_c^3 \alpha \mathcal{L}_3 \mathbb{V}_{11} e^{i k_c z}.
\end{split}
\eeq
